Project Notes

### 2020-04-10 notes/notes.tex
Notes: update 10/04/2020

@@

\begin{lstlisting}[breaklines=true, tabsize=4, frame=single]
protocol Next(role Runtime, role State) {
	// not really a `choice`, more of `based on the type of State`\dots
	choice at Runtime {
		// non-terminal
		choice at Runtime {
			// send
			PerformSend(???) from Runtime to State;
			Send(role: string, label: string, payload: any[]) from State to Runtime;

@@

		} or {
			// receive
			PrepareReceive(???) from Runtime to State;
			do Receive(Runtime, State);
		}

>>>>

\paragraph{10/04/2020}
\begin{itemize}
\item
Start formalising the encoding for states and runtime for Node targets.

@@

\begin{lstlisting}[breaklines=true, tabsize=4, frame=single]
protocol Next(role Runtime, role State) {
	// not really a `choice`, more of `based on the type of State`\dots
	choice at Runtime {
		// non-terminal
		choice at Runtime {
			// send
			PerformSend(send: ???, next: ???) from Runtime to State;
			Send(role: string, label: string, payload: any[]) from State to Runtime;

@@

		} or {
			// receive
			PrepareReceive(register: ???, next: ???) from Runtime to State;
			do Receive(Runtime, State);
		}
